Degeneracy and parameter magnitude

### 2015-03-02 Toy Example/expected value/apps/degen_magnitude.Rmd
file structure for apps

ggvis.dat %>%
  ggvis(~multiplier, ~frac_degen) %>%
  layer_points(fill = ~n_param_f) %>% 
  layer_lines(stroke = ~n_param_f) %>%
  add_axis("x", title = "Radius Multiplier") %>%
  add_axis("y", title = "Fraction Degenerate") %>%
  add_legend("fill", title = "# Parameters") %>%
  add_legend("stroke", title = "# Parameters") %>%
  handle_click(on_click)

>>>>

ggvis.dat %>%
  ggvis(~multiplier, ~frac_degen) %>%
  layer_points(fill = ~n_param_f, size.hover := 200) %>% 
  layer_lines(stroke = ~n_param_f) %>%
  add_axis("x", title = "Radius Multiplier") %>%
  add_axis("y", title = "Fraction Degenerate") %>%
  add_legend("fill", title = "# Parameters") %>%
  add_legend("stroke", title = "# Parameters") %>%
  handle_click(on_click)
